%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Init
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Structure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter*{Introduction}
\label{chap:Intro}
\renewcommand{\chapterheadstart}{~\vspace{1.7cm}\\}
\section{On the structures in our universe}
\begin{itemize}
\item Organised vs. Search view of the world. Think folders in reality and on our machines.
\item Where is structure?
\begin{itemize}
\item Morphology
\item Carnatic Music
\item Human constructed situations: spanning environments to creations and object clusters. why 
so? To help memory? Transfer of knowledge, linguistics, communication ease, data compression?
\item languages, programming or human
\end{itemize}
\item Where is there no structure?
\begin{itemize}
\item Physics models: brownian motion
\item Environment, nature
\item Random chance situations
\item But we still tried to model them with some structure. Or did we?
\end{itemize}
\item Is there really some structure or do we seek it out?
\item We assume some all of us know some coordinates, some conventions and some functional knowledge about structures, then we go about trying to model our current circumstance or technical problem in terms of structures we already know, to be able to convey that across to others.
\end{itemize} 
\section{Where is structure?}
Context is important. [Use the example from Lec 07 of Critical Perspectives of Data Science]. How is the wolf different from a dog for a DNN? The number of white pixels in the picture which signifies snow - a data skew. But wait, it has learnt from context? Can we say that? Is it true for us as well when we recognise wolves?

Stop sign with patches is misunderstood -- example. How do we still understand it? It is the context --> slippery road, junction, the functional knowledge of STOP signs and finally the allowance by knowledge for vandalism by patches by hoodlums.

\section{Why care for structure?}
\section{Machine Learning: Attention to structures - An interpretation}
\begin{enumerate}
\item Structure Learning
\item All regression and Classification are structures to predict or to bound. Structure matching?
\item What is contained in structure? Features, clarity, information
\begin{enumerate}
\item In-filling deep learning
\item word predictor NLP
\item Space partitioning for object search
\item Mapping, topological especially. Combination of planes, blobs and so on: Basis structures.
\item Compression of data: Speech coders, Spectral Band Replication
\item GP based regression
\item Decompositions?
\end{enumerate}
\end{enumerate}

%\framebox(350,300){text}