\newcommand{\llabelA}[2]{\newcounter{#2}\setcounter{#2}{\value{#1}} \expandafter\gdef\csname#2\endcsname{[\Alph{#2}]}}
\newcommand{\llabelN}[2]{\newcounter{#2}\setcounter{#2}{\value{#1}} \expandafter\gdef\csname#2\endcsname{[\arabic{#2}]}}


% -----------------------------------------------------------
\noindent
The thesis is based on the following papers:
% -----------------------------------------------------------

\newcounter{Lcount}
\begin{list}{[\Alph{Lcount}]}
{\usecounter{Lcount}%    inform the list command to use this counter
\setlength{\rightmargin}{\leftmargin}}%    set rightmargin equal to leftmargin

\item \llabelA{Lcount}{FirstPaper} \llabelA{Lcount}{Pieropan14Roman}
Alessandro Pieropan and Hedvig Kjellstr{\"o}m.
\newblock Unsupervised Object Exploration Using Context.
\newblock In \emph{Proceedings of the 2014 IEEE International Symposium on Robot and Human Interactive Communication (ROMAN'14)}, Edinburgh, UK, August 2014.

\item \llabelA{Lcount}{SecondPaper} \llabelA{Lcount}{Pieropan15ICRA}
Alessandro Pieropan, Niklas Berstr{\"o}m, Masatoshi Ishikawa and Hedvig Kjellstr{\"o}m.
\newblock Robust 3D Tracking of Unknown Objects.
\newblock In \emph{In submission to 2015 IEEE/RSJ International Conference on Robotics and Automation (ICRA'15)}, Seattle, USA, May 2015.

\item \llabelA{Lcount}{ThirdPaper} \llabelA{Lcount}{Pieropan13ICRA}
Alessandro Pieropan, Carl Henrik Ek and Hedvig Kjellstr{\"o}m.
\newblock Functional Object Descriptors for Human Activity Modeling.
\newblock In \emph{Proceedings of the 2013 IEEE/RSJ International Conference on Robotics and Automation (ICRA'13)}, Karlsruhe, Germany, May 2013.

\item \llabelA{Lcount}{FourthPaper} \llabelA{Lcount}{Pieropan14Humanoids}
Alessandro Pieropan, Carl Henrik Ek and Hedvig Kjellstr{\"o}m.
\newblock Recognizing Object Affordances in Terms of Spatio-Temporal Object-Object Relationships.
\newblock In \emph{Proceedings of the 2014 IEEE/RAS International Conference on Humanoid Robots (HUMANOIDS'14)}, Madrid, Spain, November 2014.

\item \llabelA{Lcount}{FifthPaper} \llabelA{Lcount}{Pieropan14IROS}
Alessandro Pieropan, Giampiero Salvi, Karl Pauwels and Hedvig Kjellstr{\"o}m.
\newblock Audio-Visual Classification and Detection of Human Manipulation Actions.
\newblock In \emph{Proceedings of the 2014 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS'14)}, Chicago, USA, September 2014.

\end{list}




% -----------------------------------------------------------
% -----------------------------------------------------------
% -----------------------------------------------------------
% -----------------------------------------------------------
\endinput

